\documentclass[11pt, oneside]{article}
\usepackage[margin=0.4in]{geometry}
\geometry{letterpaper}
\usepackage[parfill]{parskip}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{fontawesome}
\pagecolor{white}
\usepackage[colorlinks=true, linkcolor=blue, urlcolor=blue]{hyperref}
\pagestyle{empty}

\title{Fabricio Sperotto Sffair}
\author{Fabricio Sperotto Sffair}

\begin{document}

\begin{center}
    \section*{Fabricio Sperotto Sffair, Senior iOS Engineer}
    
    \href{https://www.linkedin.com/in/fabriciosffair/}{\faLinkedin \quad} \href{https://github.com/fabriciosffair}{\faGithub \quad}
    \href{mailto:fabriciosffair@gmail.com}{fabriciosffair@gmail.com}
\end{center}

\section*{Profile}

Experienced Mobile Developer with 7+ years of industry experience driving business results and leading innovative projects. At AirApps, my contributions developing applications and managing teams helped increase annual revenue by \$18 million.

\section*{Skills}

\begin{itemize}
    \item \textbf{iOS}: Swift, Objective-C, SwiftUI, UIKit, , XCTest, Snapshot, Core Location, Core Bluetooth, Core Motion, UserDefaults, Keychain, CoreData, SwiftData, Combine, Concurrency, MVVM, TDD, Machine Learning, SPM, CocoaPods, REST API, MQTT
    \item \textbf{General}:  Management, Team building, Leadership Git, CI/CD, Bitrise, Jenkins, Github Actions, Xcode Cloud), Jira, Scrum, Analytics, A/B Testing, Feature Flag, AI
\end{itemize}

\section*{Experience}

\textbf{\href{https://www.medicalgorithmics.com}{Medicalgorithmics} - Poland - Remote}
\hfill
\textit{2023 - Present}

\textbf{Senior iOS Engineer}

\begin{itemize}
    \item Led the development efforts, creating an iPadOS and macOS solution for initializing a BLE ECG device using CoreBluetooth and visualizing real-time ECG Signals using SwiftUI, Combine, applying SOLID principles modularizing the app using SPMs, XCTests for Unit tests achieving test coverage of 75\%  and implemented CI/CD using Xcode Cloud.
    \item Managed project progress and ensure timely delivery of features and updates, in Kanban agile environment.
    \item Implementation of PyTorch integration, to leverage the use of AI on-device.
\end{itemize}


\textbf{\href{https://www.biometryks.com}{Biometryks} - United States - Remote}
\hfill
\textit{2021 - 2023}

\textbf{Lead iOS Engineer}

\begin{itemize}
    \item Led development efforts on iOS/MacOS App from scratch, integrating with a BLE sensor using CoreBluetooth, applying SOLID principles modularizing the app using SPMs, XCTests for Unit tests and implemented CI/CD using Xcode Cloud.
    \item Led Development efforts on iOS/WatchOS app from scratch for research in health industry, using SwiftUI for the UI, CoreMotion to detect gyroscope, motion, magnetometers and acceloremeters events.
    \item Managed project progress and ensure timely delivery in Kanban agile environment
\end{itemize}

\textbf{\href{https://airapps.co}{Air Apps} - United States - Remote}

\textbf{Engineering Manager}
\hfill
\textit{2022 - 2023}

\begin{itemize}
    \item Managed teams of 5 iOS engineers, maintaining recurring 1-1’s, with continuous feedback and career mentoring. 
    \item Maintained existing apps with 170k+ subscribed active users - Translate Now, Hello AI, Fonts Air with over \$40M annual revenue
    \item Closely worked to the C-Level and product team to create year roadmap and provide technical input on decision making.
\end{itemize}

\textbf{Staff iOS Engineer}
\hfill
\textit{2022 - 2022}

\begin{itemize}
    \item Identified and solved development bottlenecks, process and continuously timely deliver iOS app MVPs using SwiftUI, MVVM architecture, SOLID principles, and maintaining CI/CD pipeline using Bitrise;
    \item Developed a 6 apps from scratch within tight deadlines of 1 month, contributing to company goals, which helped the increase of +\$15M annual revenue.
    \item Developed new features for existing apps with large user base in SwiftUI, UIKit, Clean Architecture, MVVM and XCTests for Unit Tests;
\end{itemize}

\textbf{\href{https://dellentconsulting.com}{Dellent} - Portugal - Remote}
\hfill
\textit{2021 - 2022}

\textbf{Senior iOS Engineer }

\begin{itemize}
    \item Developed new features and maintained \href{https://www.dunelm.com}{Dunelm} Mobile Point of Sale enterprise app in Swift using SwiftUI, MVVM, XCTests for unit tests in Agile environment SCRUM;
    \item Increased test coverage from 53\% to 71\%, guaranteeing core functionalities to work as expected;
    \item Automated enterprise deployment process for MS Intune, increasing deployment efficiency and decreasing average time from 30minutes to 12minutes;
\end{itemize}

\textbf{Tribalscale - Canada - Remote}
\hfill
\textit{2021 - 2021}

\textbf{Senior iOS Engineer}

\begin{itemize}
    \item Developed and maintenance Ford Autonomous Vehicle Test as a Service iOS app, in Swift. UI developed using SnapKit and SwiftUI. , MapKit and CoreLocation were used for the map to display location of autonomous car and the current location of the user requesting ride.
    \item Agile environment using XP taking advantage of pair programming.
\end{itemize}

\section*{Education}
\textbf{UniRITTER}
\hfill
\textit{BSc in Computer Science - 2021 - 2024}

\end{document}